### 2017-02-13 CO750-ApproximationAlgorithmsTopics/assignments/assignment_01.tex
Proofreading A1 of apxalgs

Let $S$ be the set of edges returned by the greedy algorithm. Order the edges as $S = \{e_1, \dots, e_n\}$ in the order they were taken during the operation of $\cA$. Let $F_i := E\backslash \tilde{E}$ be the edges removed from $E$ at the edge of iteration $i$ of $\cA$ (the iteration where $e_i$ is added to $S$). Let $S^*$ be the optimal solution and partition $S^* = S^*_1 \cup \dots \cup S^*_n$ where $S^*_i = S^* \cap F_i$.

@@

We proceed by induction. For $e_1$ $\{e_1\}$ is inclusion-wise maximal on $\cS[F_1]$ (by definition of $F_1$), and $S_1^*$ is feasible on $\cS[F_1]$ since $S^*_1 \subseteq F_1$ and $S^* \in \cS$. Thus we have $|\{e_1\}| \geq \frac{1}{2} |S_1^*|$, and hence

@@

Suppose that the claim holds for $S^*_1 ,\dots, S^*_i$. Now by our greedy choice, and induction, $w_{e_{i+1}} \geq w_{e_j} \geq w_e$ for all $e \in S^*_j$ for all $j = 1,\dots, i$. So when $\cB$ redistributes edges of $S^*_{i+1}$ the cost property on the earlier sets is not violated. Also by our greedy choice, any edges that were not moved from $S^*_{i+1}$ by $\cB$ have cost at most $w_{e_{i+1}}$. To finish the proof of the claim, we demonstrate that while $|S_{i+1}^*| > \alpha$ there exists some $S^*_j$ with $j\leq i$ and $|S^*_j| < 2$. Observe that $\{e_1, \dots, e_{i+1}\}$ is inclusion-wise maximal on $\cS[F_1 \cup \dots \cup F_{i+1}]$ by definition of $F_1 \cup \dots \cup F_{i+1}$. Also $\bigcup_{j=1}^{i+1} S^*_j \in \cS[F_1 \cup \dots \cup F_{i+1}]$ so we have that

@@

We proceed by induction. For $e_1$ $\{e_1\}$ is inclusion-wise maximal on $\cS[F_1]$ (by definition of $F_1$), and $S_1^*$ is feasible on $\cS[F_1]$ since $S^*_1 \subseteq F_1$ and $S^* \in \cS$. Thus we have $|\{e_1\}| \geq \frac{1}{\alpha} |S_1^*|$, and hence

@@

The fact that the Greedy Algorithm runs in polynomial time is obvious. $|E(v,S)|$ can be computed in $O(|E|)$ time and the while loop runs for $O(|V|)$ iterations. Further it clearly returns a cut. It remains to verify the approximation factor of $\frac{1}{2}$ holds.

@@

We show that the approximation factor is maintained throughout operation of the algorithm on the graph $G[V\backslash \bar{V}]$ induced by vertices considered so far. After the first iteration only one vertex has been considered and the approximation factor holds trivially on the graph induced by that one vertex. Now for induction let $V' = V \backslash \bar{V}$ be the set of vertices considered so far by the Greedy Algorithm, and at the start of the next iteration the vertex $v \in V$ is being considered. Let $S \subseteq V$ be the cut set considered so far, and let $S^*$ be the optimal cut set on $G[V']$. Let $\bar{S} = V'\backslash S$ and $\bar{S^*} = V' \backslash S^*$. We may assume without loss of generality that the Greedy Algorithm puts $v \in S$ and the optimal solution puts $v \in S^*$ after this iteration (if this does not hold simply relabel $S$ with $\bar{S}$ below, or $S^*$ with $\bar{S^*}$ with respect to which assumption does not hold). 

@@

Now observe that for all $i = 1,\dots, k$, $\delta(S^*_i) \subseteq E(G_i)$, hence in particular $\delta(S^*) \subseteq E(G_i)$. Thus $|\delta(S^*)|$ has size at most that of an optimal cut in $G_i$. Now by our choice of $V_i$, using $2$-approximation algorithm $\cB$, $2|\delta(V_i)|$ is at the size of an optimal cut in $G_i$. Hence we have

@@

Now to see the approximation factor holds let $\cS^i$ denote the solution maintained by $\cA$ at the end of iteration $i$. Then the returned solution is $\cS^{k}$. Let $\cO$ be an optimal solution. Observe from Lemma \ref{lemma:3b1} that $c(\cS^{i}) \geq \frac{1}{2k} c(\cO) + (1- \frac{1}{2k})c(S^{i-1})$. We will apply this inequality inductively to achieve the bound:

@@

We first observe that this $IP$ is easy to solve on trees. Indeed let $T$ be a tree, and for every $uv \in E(T)$ let $S^{uv}_u$ denote the set of vertices in connected component of $T-uv$ containing $u$, and define $S^{uv}_v$ similarly. By definition, $\delta(S^{uv}_u) =  \{e\} = \delta(S^{uv}_v)$. We define the following algorithm $\cA$ to solve $IP$ on a tree $T$:

@@

To see $(1)$, it is immediate from the definition of $f$ that $x \geq 0$. It remains to verify the cut inequalities. Let $S \subseteq V$. Enumerate $\delta(S)$ as $\delta(S) = \{e_1, \dots, e_k \}$, where each $e_i := u_iv_i$ and $u_i \in S$. Let $S_1, \dots, S_\ell$ be the partition of $S$ induced by the connected components of $G-\delta(S)$ contained in $S$.  Now let $D(S_i) = \{ e_j \in \delta(S) : u_j \in S_i \}$ be the set of edges in $\delta(S)$ incident with $S_i$. Notice that the set of $D(S_i)$ partition $\delta(S)$. 

@@

&\leq \sum_{i=1}^\ell \sum_{e_j \in D(S_i)} f(V\backslash S^{e_j}_{u_j}) &\text{by subadditivity} \\ t

@@

d^T(u,v) &= d^T(S_i, S^u_{i-1}) + d^T(S_, S^u_{i-1}) + d^T(S^u_{i-1}, u) + d^T(S^v_{i-1}, v)\\

@@

We first analyze $Pr[B]$. Without loss we may assume $d(c,u) \leq d(c,v)$. For $c$ to cut $u,v$ we need $d(c,u) \leq 2^\beta 2^{i-1} < d(c,v)$ by definition.  Since we sample $2^\beta$ uniformly at random, the probability of this happening is simply $\frac{1}{2^{i-1}}$ times the length of the interval intersecting $[2^{i-1},2^i]$ with $[d(c,u), d(c,v)]$. More formally:

>>>>

Let $S$ be the set of edges returned by the greedy algorithm. Order the edges as $S = \{e_1, \dots, e_n\}$ in the order they were taken during the operation of $\cA$. Let $F_i := E\backslash \tilde{E}$ be the edges removed from $E$ at the end of iteration $i$ of $\cA$ (the iteration where $e_i$ is added to $S$). Let $S^*$ be the optimal solution and partition $S^* = S^*_1 \cup \dots \cup S^*_n$ where $S^*_i = S^* \cap F_i$.

@@

We proceed by induction. For the base case $e_1$, $\{e_1\}$ is inclusion-wise maximal on $\cS[F_1]$ (by definition of $F_1$), and $S_1^*$ is feasible on $\cS[F_1]$ since $S^*_1 \subseteq F_1$ and $S^* \in \cS$. Thus we have $|\{e_1\}| \geq \frac{1}{2} |S_1^*|$, and hence
$$|S^*_1| \leq 2.$$

@@

Suppose that the claim holds for $S^*_1 ,\dots, S^*_i$. Now by our greedy choice, and induction, $w_{e_{i+1}} \geq w_{e_j} \geq w_e$ for all $e \in S^*_j$ for all $j = 1,\dots, i$. So when $\cB$ redistributes edges of $S^*_{i+1}$ the cost property on the earlier sets is not violated. Also by our greedy choice, any edges that were not moved from $S^*_{i+1}$ by $\cB$ have cost at most $w_{e_{i+1}}$. To finish the proof of the claim, we demonstrate that while $|S_{i+1}^*| > 2$ there exists some $S^*_j$ with $j\leq i$ and $|S^*_j| < 2$. Observe that $\{e_1, \dots, e_{i+1}\}$ is inclusion-wise maximal on $\cS[F_1 \cup \dots \cup F_{i+1}]$ by definition of $F_1 \cup \dots \cup F_{i+1}$. Also $\bigcup_{j=1}^{i+1} S^*_j \in \cS[F_1 \cup \dots \cup F_{i+1}]$ so we have that

@@

We proceed by induction. For the base case $e_1$, $\{e_1\}$ is inclusion-wise maximal on $\cS[F_1]$ (by definition of $F_1$), and $S_1^*$ is feasible on $\cS[F_1]$ since $S^*_1 \subseteq F_1$ and $S^* \in \cS$. Thus we have $|\{e_1\}| \geq \frac{1}{\alpha} |S_1^*|$, and hence

@@

To see that the Greedy Algorithm runs in polynomial time observe that $|E(v,S)|$ can be computed in $O(|E|)$ time and the while loop runs for $O(|V|)$ iterations. Further the algorithm returns a feasible solution by definition. It remains to verify the approximation factor of $\frac{1}{2}$ holds.

@@

We show that the approximation factor is maintained throughout operation of the algorithm on the graph $G[V\backslash \bar{V}]$ induced by vertices considered so far. After the first iteration only one vertex has been considered and the approximation factor holds trivially on the graph induced by that one vertex. Now for induction let $V' = V \backslash \bar{V}$ be the set of vertices considered so far by the Greedy Algorithm, and at the start of the next iteration the vertex $v \in V$ is being considered. Let $S \subseteq V$ be the cut set considered so far, and let $S^*$ be the optimal cut set on $G[V']$. Let $\bar{S} = V'\backslash S$ and $\bar{S^*} = V' \backslash S^*$. We may assume without loss of generality that the Greedy Algorithm puts $v \in S$ and the optimal solution puts $v \in S^*$ after this iteration (if this does not hold simply interchange $S$ with $\bar{S}$ below, or $S^*$ with $\bar{S^*}$ with respect to which assumption does not hold). 

@@

Now observe that for all $i = 1,\dots, k$, $\delta(S^*_i) \subseteq E(G_i)$, hence in particular $\delta(S^*) \subseteq E(G_i)$. Thus $|\delta(S^*)|$ has size at most that of an optimal cut in $G_i$. Now by our choice of $V_i$, using $2$-approximation algorithm $\cB$, $2|\delta(V_i)|$ is at most the size of an optimal cut in $G_i$. Hence we have

@@

Now to see the approximation factor holds let $\cS^i$ denote the solution maintained by $\cA$ at the end of iteration $i$. Then the returned solution is $\cS^{k}$. Let $\cO$ be an optimal solution. Observe from rewriting Lemma \ref{lemma:3b1} that $c(\cS^{i}) \geq \frac{1}{2k} c(\cO) + (1- \frac{1}{2k})c(S^{i-1})$. We will apply this inequality inductively to achieve the bound:

@@

We first observe that this $IP$ is easy to solve on trees. Indeed let $T$ be a tree, and for every $uv \in E(T)$ let $S^{uv}_u$ denote the set of vertices in the connected component of $T-uv$ containing $u$, and define $S^{uv}_v$ similarly. By definition, $\delta(S^{uv}_u) =  \{e\} = \delta(S^{uv}_v)$. We define the following algorithm $\cA$ to solve $IP$ on a tree $T$:

@@

To see $(1)$, it is immediate from the definition of $f$ that $x \geq 0$. It remains to verify the cut inequalities. Let $S \subseteq V$. Enumerate $\delta(S)$ as $\delta(S) = \{e_1, \dots, e_k \}$, where each $e_i := u_iv_i$ and $u_i \in S$. Let $S_1, \dots, S_\ell$ be the partition of $S$ induced by the connected components of $G-\delta(S)$ contained in $S$.  Now let $D(S_i) = \{ e_j \in \delta(S) : u_j \in S_i \}$ be the set of edges in $\delta(S)$ incident with $S_i$. Notice that $\{D(S_i): i = 1\dots \ell\}$ is a partition of $\delta(S)$. 

@@

&\leq \sum_{i=1}^\ell \sum_{e_j \in D(S_i)} f(V\backslash S^{e_j}_{u_j}) &\text{by subadditivity} \\ 

@@

d^T(u,v) &= d^T(S_i, S^u_{i-1}) + d^T(S_i, S^v_{i-1}) + d^T(S^u_{i-1}, u) + d^T(S^v_{i-1}, v)\\

@@

We first analyze $Pr[B]$. Without loss we may assume $d(c,u) \leq d(c,v)$. For $c$ to cut $u,v$ we need $d(c,u) \leq 2^\beta 2^{i-1} < d(c,v)$ by definition.  Since we sample $2^\beta$ uniformly at random, the probability of this happening is simply $$\frac{1}{2^{i-1}}$$ times the length of the interval intersecting $[2^{i-1},2^i]$ with $[d(c,u), d(c,v)]$. More formally:
